---
title: "Ch1 exploratory figures subset"
author: "Camilla Seirup"
date: "2023-10-15"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
```

```{r import, include = FALSE, cache = FALSE}
#do I need to load data here if it's in the compile script?
```

```{r deps, include = FALSE}
library(tidyverse)
library(forestNETN)
library(htmltools)
library(knitr)
library(kableExtra)
library(ggalt)
```

```{r compile_data, include = FALSE}
source("davis_functions.R")
source("03_Ch1_exploratory.R")
source("AgeStructure_DisturbanceChrono.R")
```

## Summary Figures

```{r, echo=FALSE, warning=FALSE, out.height="100%", fig.height = 4.5, fig.width = 7.5}
print(Comp_tree_dist_plot)
```

Figure 2. Stem density distributions from the 1959 sampling and 2020-2022 resampling of seven spruce dominated stands in Acadia National Park, Mount Desert Island, Maine. The figure shows tree density by diameter at breast height at 10 cm increments. The smallest increment, 2.5 to 10 cm, was constrained by historic sampling methods.

```{r, echo=FALSE, warning=FALSE, out.height="100%", fig.height = 4.5, fig.width = 7.5}
#print(Log10_tree_dist_plot) #Figure 2b. Log10 stem density distributions from the 1959 sampling and 2020-2022 resampling to better determine the shape of the curve. Likely not needed?

```


```{r, echo=FALSE, out.height="100%", fig.width = 10.6}
#print(stem_mapV)#Figure 3. Stem maps for the 2020-2022 sampling events.
```



```{r, echo=FALSE, out.height="100%", fig.width = 10.6}
#print(sap_map)#Figure 4. Sapling (1 cm to 9.9 cm DBH) density heat maps per site for 2020-2022 visits. WP is not included. 
```


```{r, echo=FALSE, warning=FALSE}
#print(Comp_tree_dist_bar) 
```

```{r, echo=FALSE, out.height="100%", fig.width = 10.6}
print(treesap_map)
```

Figure 4. Tree stem map and sapling heat map combined. 


```{r, echo=FALSE, out.height="100%", fig.width = 10.6}
print(Box_den)
```
Figure 6. Bootstrapped distribution of 2020s trees: 5 10x10m subplots iterated 1000 times. 1959 and the density calculated for the full plot are included. Only live trees >10cm.

```{r, echo=FALSE, out.height="100%", fig.width = 10.6}
print(Box_BA)
```
Figure 7. Bootstrapped distribution of 2020s trees: 5 10x10m subplots iterated 1000 times. 1959 and the basal area calculated for the full plot are included. Only live trees >10cm.

```{r, echo=FALSE, out.height="100%", fig.width = 10.6}
#print(Box_bio) #Figure 8. Bootstrapped distribution of 2020s trees: 5 10x10m subplots iterated 1000 times. 1959 and the biomass calculated for the full plot are included. Only live trees >10cm.
```

## Species composition figures

```{r, echo=FALSE, fig.height= 10.6, fig.width=10.6}
print(spComp3)
```

Figure 5. Change in tree species composition by site and developmental stage. Trees are live individuals >10 cm DBH. Saplings are live individuals >= 2.5 cm and < 10 cm DBH. Seedlings are established individuals <2.5 DBH.  In 2020s, established was defined as > 15cm tall. The 4 most abundant species per site, visit, and  developmental stage were included.

```{r, echo=FALSE, fig.height= 10.6, fig.width=10.6}
print(pTSS)
```

Figure #. Relative percent change in species composition in trees, saplings, seedlings across all sites. Percent change is in basal area per hectare for trees and saplings and seedlings is percent change in density per square meter. All species included.

```{r, echo=FALSE, fig.height= 10.6, fig.width=10.6}
print(pTSSgr)
```

Figure #. Relative percent change in species composition in trees, saplings, seedlings across all sites. Percent change is in basal area per hectare for trees and saplings and in density per square meter for seedlings. Less common species grouped.


```{r, echo=FALSE, fig.width=10.6}
print(pTreeSp)
```
Figure X. Tree species composition

```{r, echo=FALSE, fig.width=10.6}
print(pSapSp)
```
Figure X. Sapling species composition

```{r, echo=FALSE, fig.width=10.6}
print(pSeedSp)
```
Figure X. Seedling species composition

##Dendro figures

```{r, echo=FALSE, out.height="100%", fig.width = 10.6}
print(ageD)
```
Figure 10. Recruitment age distributions, including Davis cores.

```{r, echo=FALSE, out.height="100%", fig.height = 10.6, fig.width = 10.6, warning=FALSE}
print(DistPlotAnn2)
```
Figure 9a. Disturbance chronology. Orange and blue bars are disturbance signal by type per year. Grey bars are releases binned by decade. Solid black line is a kernel density function. Dotted black line is the sample depth. Vertical dashed gray line indicates the year the sample depth falls to five cores. 

```{r, echo=FALSE, out.height="100%", fig.height = 10.6, fig.width = 10.6, warning=FALSE}
print(DistPlotPMPool2)
```
Figure 9b. Disturbance chronology. Orange and blue bars are disturbance signal by type per year. Grey bars are releases binned by decade. Solid black line is a kernel density function. Dotted black line is the sample depth. Vertical dashed gray line indicates the year the sample depth falls to five cores. *PM TSCA pooled with PM PIRU*.

## Tables
Table 1. Location description information for the seven sites included in the study.

```{r, echo=FALSE}
kable(dSites, format = 'html', align = 'c') %>% 
            kable_styling(fixed_thead = TRUE, bootstrap_options = 'condensed', 
                          full_width = FALSE, position = 'left', font_size = 12.5)
             
```


Table 2. Density, basal area, biomass, and carbon mass calculated for each site and sampling event. All live trees > 10cm were included. Biomass is an estimate of above ground biomass. **Should we report 2020s sample including snags?**  Plot size for 1959 sample was 500 m$^2$. Plot size in 2020-2022 was 2000 m$^2$.

```{r, echo=FALSE}
kable(SumTable_ha6, format = 'html', align = 'c',
                  col.names = c("Site", "1959", "2020s", "1959", "2020s", 
                                "1959", "2020s", "2020s", "1959", "2020s", "2020s")) %>% 
            kable_styling(fixed_thead = TRUE, bootstrap_options = 'condensed', 
                          full_width = FALSE, position = 'left', font_size = 12.5) %>%
            #column_spec(c(2,4,6), color = "#74c476", border_left = TRUE) %>% 
            #column_spec(c(3,5,7,8), color = "#006d2c") %>% 
            add_header_above(c("", "Density (stems/ha)" = 2, "Basal area (m$^2$/ha)" = 2, 
                               "Biomass (Mg/ha)" = 2, "Sapling (stems/ha)" = 2, "SDW Basal area (m$^2$/ha)" = 1,
                               "DWD Vol. (m$^3$/ha)" = 1),
                               extra_css = "border-bottom: 1px solid #000000; border-right: 3px solid #ffffff;",
                               line = FALSE) 
```

Table 3. Increment cores collected per site and the interseries correlation coefficient after cross-dating.

```{r, echo=FALSE}
kable(sCores, format = 'html', align = 'c') %>% 
            kable_styling(fixed_thead = TRUE, bootstrap_options = 'condensed', 
                          full_width = FALSE, position = 'left', font_size = 12.5)
             
```